How Toronto's homeless death toll over the years shows the dangers of addiction's epidemic?

### 2024-01-25 outputs/paper/paper.qmd
deleted model

To examine the impact of the COVID-19 pandemic on the drug poisoning
crisis, this article is divided into the following sections: data,
results, discussion, and conclusion. In the data section, I discuss the
nature of the spreadsheets obtained through the City of Toronto's
OpenDataToronto (Toronto Public Health 2023) and the steps I took to
clean and analyze the data. The Results section displays the trends
discovered during the analysis, and the Discussion section evaluates the
trends and provides insights. Finally, the conclusion summarizes the
main findings of this paper.

@@

                      caption = "Sample Table for Toronto Homeless Death")
  # Print the table

@@

```{r}
total_count_age_data <- toronto_homeless_death %>%
  group_by(Age_group, Cause_of_death) %>%
  summarise(total_count_age = sum(Count), .groups = 'drop')
sample_total_count_by_age_data <- head(total_count_age_data, 6)
knitr::kable(sample_total_count_by_age_data,'markdown',col.names = c("Age Group", "Cause of Death", "Total Count"),align = 'c',

@@

```{r}
total_count_data <- toronto_homeless_death %>%
  group_by(Year.of.death, Cause_of_death) %>%
  summarise(total_count = sum(Count), .groups = 'drop')
sample_total_count_by_year_data <- head(total_count_data, 6)
knitr::kable(sample_total_count_by_year_data,'markdown',col.names = c("Year of Death", "Cause of Death", "Total Count"),align = 'c',

@@

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to
investigate... Background details and diagnostics are included in
[Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft.
Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both
measured in millimeters.

```{=tex}
\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}
```
We run the model in R [@citeR] using the `rstanarm` package of
@rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time
spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance
$\theta$.

Our results are summarized in @tbl-modelresults. #\| echo: false #\|
eval: true #\| warning: false #\| message: false

library(rstanarm)

first_model \<- readRDS(file =
here::here("outputs/models/first_model.rds"))

#\| echo: false #\| eval: true #\| label: tbl-modelresults #\| tbl-cap:
"Explanatory models of flight time based on wing width and wing length"
#\| warning: false

modelsummary::modelsummary( list( "First model" = first_model ),
statistic = "mad", fmt = 2 )

>>>>

To examine the impact of the COVID-19 pandemic on the drug poisoning
crisis, this article is divided into the following sections: data,
results, discussion, and conclusion. In the data section, I discuss the
nature of the spreadsheets obtained through the City of Toronto's
OpenDataToronto (Toronto Public Health 2023) and the tables I obtained
for analyzing the data. The Results section displays the trends
discovered during the analysis, and the Discussion section evaluates the
trends and provides insights. Finally, the conclusion summarizes the
main findings of this paper.

@@

                      caption = "Sample Table of Toronto Homeless Death")
  # Print the table

@@

Table 2 provides the total number of deaths summarized by age group and
cause of death in the dataset, outlining the key variables available for
analysis: cause of death, age group and number of deaths.

```{r}
#| warning: false
#| message: false
#| echo: false
total_count_age_data <- toronto_homeless_death %>%
  group_by(Age_group, Cause_of_death) %>%
  summarise(total_count_age = sum(Count), .groups = 'drop')
sample_total_count_by_age_data <- head(total_count_age_data, 6)
knitr::kable(sample_total_count_by_age_data,'markdown',col.names = c("Age Group", "Cause of Death", "Total Count"),align = 'c',

@@

Table 3 provides the total number of deaths in the data set summarized
by year of death and cause of death, outlining the key variables in the
analysis of addiction harm to homeless people: cause of death, time of
death, and number of deaths.

```{r}
#| warning: false
#| message: false
#| echo: false
total_count_data <- toronto_homeless_death %>%
  group_by(Year.of.death, Cause_of_death) %>%
  summarise(total_count = sum(Count), .groups = 'drop')
sample_total_count_by_year_data <- head(total_count_data, 6)
knitr::kable(sample_total_count_by_year_data,'markdown',col.names = c("Year of Death", "Cause of Death", "Total Count"),align = 'c',

@@
